Dependent Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-12 main.tex
Add research memo.
Correcting abstract.

\newcommand{\red}[1]{\textcolor{red}{ #1 }}
\newcommand{\blue}[1]{\textcolor{blue}{ #1 }}

\begin{document}
%
\title{Contribution Title\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Akira Kawata\inst{1} \and
Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
\email{akira@kuis.kyoto-u.ac.jp} \and
\email{igarashi@kuis.kyoto-u.ac.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Multistage programming is a scheme of programming which enable us to generate codes at runtime.
And it is important to ensure the quality of generated codes.
In this paper, we extended existing multistage programming language by Hanada and Igarashi with dependent type.
This extention

>>>>

\newcommand{\red}[1]{\textcolor{red}{ #1 }}
\newcommand{\blue}[1]{\textcolor{blue}{ #1 }}
\newcommand{\TW}{\triangleright}

\begin{document}
%
\title{Dependent Typed Multi-Stage Calculus\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Akira Kawata\inst{1} \and
Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
\email{akira@fos.kuis.kyoto-u.ac.jp} \and
\email{igarashi@kuis.kyoto-u.ac.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
We develop yet another typed multi-stage calculus $\lambda^{\textrm{MD}}$.
It extends Hanada and Igarashi's $\lambda^{\triangleright\%}$ with dependent type.

Dependent types is types dependent on values. 
Vectors with lengths is famous example of dependent types and they enable us to omit boundary checking.

A multi-stage calculus enables us to generate and execute codes at runtime.
It can improve the performance of programs by generating optimized codes for given inputs.

In this paper, we design $\lambda^{\textrm{MD}}$ by introducing dependent type into $\lambda^{\TW\%}$.
You can make more efficient programs from existing dependent typed programs with $\lambda^{\textrm{MD}}$.

It has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, strong normalization and progress.

The main technical points of this paper is how to deal with Cross Stage Persistence of multi-stage calculuses in a dependent type system.
CSP is a function of a multi-stage calculus which allows to use a value in quoted code.

The first point is CSP in kinding rules.
$\lambda^{\TW\%}$ contains kinding rules because dependent types need them.

The second point is CSP in equivalence rules.
